Refinements for open automata

### 2022-07-12 2021-Refinement/paper/refinementarticle.tex
proof in progess

Let's consider any $s_{2p} \in (s_{2p})^{p\in P}$. According to the refinement relation between  $A_1$ and $A_2$ and Definition \ref{def:preservation} we have:

@@

Furthermore, according to the refinement relation between  $A_2$ and $A_3$ and Definition \ref{Def:OA-Refinement} we have  for any open transition $t_{2px}$ in $T_2$ originating from $s_{2p}$ the following:
\begin{align*}
\OTx{2p}{x}{2px}{2px} \in \fOT{s_{2p}}
\end{align*}
there exists an indexed family of OTs originating from $s_3$: 
\begin{align*}
\mpar{\OTx{3}{py}{3py}{3py} \in \fOT{s_3}}^{y \in Y} 
\end{align*}
such that $\forall y \in Y, J'_{2p} \cap H = J'_{3py} \cap H$ and
\begin{multline*}
%\everymath{\displaystyle}
V_2 \uplus V_3 \uplus \fvars{t_{2p}} \vdash\\
R_{23}\mpar{s_{2p}, s_{3}} \wedge g_{2p} \implies  \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			 \alpha_{2p}=\alpha_{3py} \wedge \bigwedge_\subbox{j \in J'_{3py} \cap H} \beta_{2pj}=\beta_{3pyj} \nwedge \\
			g_{3py} \wedge R_{23}\mpar{s'_{2p}, s'_{3y}}\psubst{\psi_{2p} \uplus \psi_{3py}}
		\end{array}}  
\end{multline*}

>>>>

Let's consider any $s_{2p} \in (s_{2p})^{p\in P}$. According to the refinement relation between  $A_1$ and $A_2$ we have the following:

@@

Yet according to the refinement  relation between   $A_2$ and $A_3$ the following is satisfied:
\begin{multline*}
\bigforall \mpar{s_{2p}, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_{2p}, t_3} = \mpar{\OTx{2p}{}{2p}{2p}, \OTx{3}{}{3}{3}} \in \fOT{s_{2p}} \times \fOT{s_3} \\ 
\bigsymb{\bigexists} 
\mpar{t_{2px} = \OTx{2p}{x}{2px}{2px} \in \fOT{s_{2p}}}^{y \in Y},
V_2 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{2px}} \uplus \fvars{t_3} \uplus \fvars{t_{2p}} \vdash \hspace{6cm}\\  R_{23}\mpar{s_2, s_3} \wedge 	g_{2p}\wedge g_3 \wedge \alpha_2 = \alpha_3 
%\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2pj} = \beta_{3j} 
\implies \hspace{6cm}\\
%\exists
%\OTx{1}{a}{3}{3}\in \fOT{s_2}. \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
\alpha_{2p}=\alpha_{2p x}  \land J'_{2px}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2xj}\land g_{2p x}\land
 R_{23}\mpar{s'_{2p x}, s'_3}\psubst{\psi_{2p x} \uplus \psi_3}}\\
\end{multline*}

For any open transition $t_{2px}$ originating from $s_{2p}$ we have 
the following by definition of refinement between  $A_2$ and $A_3$:

\begin{align*}
 \OTx{2p}{x}{2px}{2px} \in \fOT{s_{2p}} 
\end{align*}
there exists an indexed family of OTs originating from $s_3$: 
\begin{align*}
\mpar{\OTx{3}{pxy}{3pxy}{3pxy} \in \fOT{s_3}}^{y \in Y} 
\end{align*}
such that $\forall y \in Y, J'_{2px} \cap H = J'_{3py} \cap H$ and
\begin{multline*}
%\everymath{\displaystyle}
V_2 \uplus V_3 \uplus \fvars{t_{2px}} \vdash\\
R_{23}\mpar{s_{2p}, s_{3}} \wedge g_{2px} \implies  \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			 \alpha_{2px}=\alpha_{3pxy} \wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H} \beta_{2pxj}=\beta_{3pxyj} \nwedge \\
			g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
		\end{array}}  
\end{multline*}
